---
output: html_document
---

<h2> Xu and Tenenbaum 2007b Replication </h2>
====
`r as.character(format(Sys.Date(), format="%B %d, %Y"))`
======


***
***

In the present studies, we attempted to replicate Xu and Tenenbaum (2007b) in a  manipulation of the communicative context of word learning. In the weak sampling condition, the naive learner guesses about the training set of exemplars. In the strong sampling condition, a knowledgeable teacher identifies a training set of exemplars. As predicted by the model, Xu and Tenenbaum found that both adults and children overwhelmingly generalized more narrowly under strong sampling, than under weak sampling. We completed two online and an in-lab replication of this study, and found evidence for a pattern similar to the original data, but with far more variability across participant than observed in the original study.

Note here that we are using a more liberal definition of basic generalization than Xu and Tenenbaum (2007b) -- we count a generalization as basic if the participant generalization to the basic level on any basic level question.

<b> Studies: </b>  <br/>
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**[(1) Turk #1](#t1)** <br/>
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**[(2) Turk #2](#t2)** <br/>
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**[(3) In lab](#l1)** <br/>


```{r, echo = F, warning = F, include = F}

rm(list = ls())

#--Load packages--

library(knitr)
opts_chunk$set(cache = F, warning = F, message = F)
library(boot)
library(ggplot2)
library(plyr)
#source("/Documents/GRADUATE_SCHOOL/Ranalysis/useful.R")

getPs <- function(d, dv){ 
  # get proportions
  prop = sum(d==dv)/length(d)
  
  # bootstrap across subject proportion responses for each category
  b <- boot(d, function(u, i) table(u[i])[dv]/length(u), R = 1000) 
  ci <- boot.ci(b, type = "perc")  
  ciwl = ci$percent[4]
  ciwu = ci$percent[5]
  
  es <- data.frame(p = prop,
    ciwl = ciwl,
    ciul = ciwu,
    dv = dv)
  
  return (es)
  }

d.fc <- function(response, cond) {
  # http://www.meta-analysis.com/downloads/Meta-analysis%20Converting%20among%20effect%20sizes.pdf
  #https://www.medcalc.net/tests/odds_ratio.php
    response = droplevels(response)
    response<- ordered(response, levels = c( "basic", "sub"))
    cond <- ordered(cond, levels = c( "learner", "teacher"))

    #use odds ratioto calculate d
    ns = table(cond, response)
    or = (ns[1]*ns[4])/(ns[2]*ns[3]) 
    cf = sqrt(3)/pi
    effect_size = log(or) * cf #calculate d
    #effect_size = log(or)  #calculate d

    
    # caluclate 95 CI
    se = sqrt((1/ns[1]) + (1/ns[2]) + (1/ns[3]) + (1/ns[4])) # calculate se of log odds ratio
    d_se = se * (3/(pi^2)) # caclulate se of 
    d_err = d_se*1.96
    #d_err = se*1.96
    
    cill = effect_size - d_err
    ciul = effect_size + d_err
    
    es <- data.frame(effect_size=effect_size,
                     cill = cill,
                     ciul = ciul
                     )
  return (es)
  }

```


***
***

<a name="t1"/>
<h3> Turk Replication #1 </h3>

Read in data and pre-process.
```{r, echo =F}
d1 = read.csv("../data/turk_replication_1.csv")

# make factors
d1$Answer.sample <- factor(d1$Answer.sample, labels=c('teacher','learner')) # sample0= teacher, sample1=learner
d1$Answer.label <- factor(d1$Answer.label, labels=c('nolabel','label')) # 0=nolabel, 1=label

d1$Answer.Qwcheck <- factor(d1$Answer.Qwcheck)
d1$Answer.Qwsmm1 <- factor(d1$Answer.Qwsmm1)
d1$Answer.Qwsmm2 <- factor(d1$Answer.Qwsmm2)
d1$Answer.Qwsm1 <- factor(d1$Answer.Qwsm1)
d1$Answer.Qwsm2 <- factor(d1$Answer.Qwsm2)

d1$Answer.Qacheck <- factor(d1$Answer.Qacheck)
d1$Answer.Qasm1 <- factor(d1$Answer.Qasm1)
d1$Answer.Qasm2 <- factor(d1$Answer.Qasm2)
d1$Answer.Qasmm1 <- factor(d1$Answer.Qasmm1)
d1$Answer.Qasmm2 <- factor(d1$Answer.Qasmm2)
```

Filter.
```{r}
# subset data
d1 <- subset(d1, d1$Answer.label == 'label') # take out nolabel trials (study 4)
d1 <- subset(d1, !duplicated(d1$workerid)) # take out those who did it twice
d1 <- subset(d1, Answer.click1 == "\"correct\"" & Answer.click2 == "\"correct\"") # take out if selected wrong training items
d1 <- subset(d1, Answer.Qwcheck == 0) # take out if missed check generalization question
d1 <- subset(d1, Answer.question1 == 'true') # take out those who missed filter question
```


Categorize response patterns based on criterion.
```{r}
criterion = "unstrict1"  # category criterion

d1 <- d1[d1$Answer.label== "label",]
numsubj = dim(d1)[1]

if (criterion == "strict"){
  proper <- d1$Answer.Qwsmm1 == 0 & d1$Answer.Qwsmm2 == 0 & 
    (d1$Answer.Qwsm1 == 0 & d1$Answer.Qwsm2 == 0)
  sub <- d1$Answer.Qwsmm1 == 0 & d1$Answer.Qwsmm2 == 0 & 
    d1$Answer.Qwsm1 == 1 & d1$Answer.Qwsm2 == 1
  basic <- (d1$Answer.Qwsmm1 == 1 & d1$Answer.Qwsmm2 == 1) &
    d1$Answer.Qwsm1 == 1 & d1$Answer.Qwsm2 == 1 
  
} else if (criterion == "unstrict2"){
  proper <- d1$Answer.Qwsmm1 == 0 & d1$Answer.Qwsmm2 == 0 & 
    (d1$Answer.Qwsm1 == 0 & d1$Answer.Qwsm2 == 0)
  sub <- d1$Answer.Qwsmm1 == 0 & d1$Answer.Qwsmm2 == 0 & 
    (d1$Answer.Qwsm1 == 1 | d1$Answer.Qwsm2 == 1)
  basic <- (d1$Answer.Qwsmm1 == 1 | d1$Answer.Qwsmm2 == 1) &
    (d1$Answer.Qwsm1 == 1 & d1$Answer.Qwsm2 == 1)
  
} else if (criterion == "unstrict1"){
  proper <- d1$Answer.Qwsmm1 == 0 & d1$Answer.Qwsmm2 == 0 & 
    (d1$Answer.Qwsm1 == 0 | d1$Answer.Qwsm2 == 0)
  sub <- d1$Answer.Qwsmm1 == 0 & d1$Answer.Qwsmm2 == 0 & 
    d1$Answer.Qwsm1 == 1 & d1$Answer.Qwsm2 == 1
  basic <- (d1$Answer.Qwsmm1 == 1 | d1$Answer.Qwsmm2 == 1) &
    d1$Answer.Qwsm1 == 1 & d1$Answer.Qwsm2 == 1   	
  
} else if(criterion == "x&t"){
  sub <- d1$Answer.Qwsmm1 == 0 & d1$Answer.Qwsmm2 == 0 & 
    d1$Answer.Qwsm1 == 1 & d1$Answer.Qwsm2 == 1
  basic <- (d1$Answer.Qwsmm1 == 1 & d1$Answer.Qwsmm2 == 1) &
    d1$Answer.Qwsm1 == 1 & d1$Answer.Qwsm2 == 1 		
}
d1$w.ans.cat <- "other"
d1$w.ans.cat[sub] <- "sub"
d1$w.ans.cat[basic] <- "basic"
#d1$w.ans.cat[proper] <- "proper"
d1$w.ans.cat = factor(d1$w.ans.cat, levels=c("proper", "sub", "basic", "other"))
d1 = d1[d1$w.ans.cat != "other",]
# get proportions and bootstrapped CIS
M <- data.frame()

for (k in 1:length(levels(d1$w.ans.cat))){
    M = rbind(M, ddply(d1, .(Answer.sample), 
                     function (d) {getPs(d$w.ans.cat, levels(d$w.ans.cat)[k])}))
}
M$exp = "Turk #1"
```

Plot.


```{r, echo=F}
# plot
ggplot(data=M[M$dv == "basic" | M$dv == "sub",], aes(x=factor(dv), y=p, fill=Answer.sample)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_linerange(aes(ymin=ciwl,ymax=ciul), position=position_dodge(.9)) +
  ylim(0,1) +
  ylab("Prop. participants showing \ngeneralization pattern") +
  xlab("Generalization pattern") +
  ggtitle("Turk Replication #1") +
  theme(text = element_text(size=18),
        plot.title=element_text(size=20, face = "bold"),
        plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(color = 'black'),
        legend.position=c(.85,.8),
        panel.background = element_rect(fill = 'white', colour = 'white')) +
  scale_fill_discrete(name="Sampling\nCondition") 

```

Stats 
No difference.
```{r}
d1_counts= table(d1$w.ans.cat, d1$Answer.sample)[2:3,]
chisq.test(d1_counts)
```


<a name="t2"/>
<h3> Turk Replication #2 </h3>

Read in data and pre-process
```{r, echo = F}
d2 <- read.csv("../data/turk_replication_2.csv",sep="\t",header=T)

d2 <- d2[,c(-1:-19,-21:-32,-36,-41:-43,-54:-55,-56)] # remove unnecessary columns

# make factors
d2$Answer.sample <- factor(d2$Answer.sample, labels=c('teacher','learner')) # sample0 = teacher, sample1=learner

d2$Answer.Qcheck1 <- factor(d2$Answer.Qcheck1)
d2$Answer.Qcheck2 <- factor(d2$Answer.Qcheck2)

d2$Answer.Qsub1 <- factor(d2$Answer.Qsub1)
d2$Answer.Qsub2 <- factor(d2$Answer.Qsub2)

d2$Answer.Qbasic1 <- factor(d2$Answer.Qbasic1)
d2$Answer.Qbasic2 <- factor(d2$Answer.Qbasic2)
d2$Answer.Qbasic3 <- factor(d2$Answer.Qbasic3)

d2$Answer.Qproper1 <- factor(d2$Answer.Qproper1)
d2$Answer.Qproper2 <- factor(d2$Answer.Qproper2)
d2$Answer.Qproper3 <- factor(d2$Answer.Qproper3)
```

Filter.
```{r}
# subset data
d2 <- subset(d2, Answer.click1 == "\"correct\"" & Answer.click2 == "\"correct\"") # take out those who click on wrong training items
d2 <- subset(d2, Answer.Qcheck1 == 0 & Answer.Qcheck2 == 0) # take out if missed check generalization question
d2 <- subset(d2, Answer.question1 == 'true' & Answer.question2 =='true' & 
  Answer.question3 == 'true' & Answer.question4=='true' ) # take out those who missed filter question

```

Categorize response patterns based on criterion.
```{r}
criterion = "unstrictnew" 
numsubj = dim(d2)[1]

if (criterion == "unstrictold"){
  proper <- (d2$Answer.Qproper1 == 1 & d2$Answer.Qproper2 == 1 & 
  	d2$Answer.Qproper3 == 1) & d2$Answer.Qsub1 == 0 &
		d2$Answer.Qsub2 == 0 & d2$Answer.Qbasic1 == 0 &
		d2$Answer.Qbasic2 == 0 & d2$Answer.Qbasic3 == 0 
	sub <- 	d2$Answer.Qproper1 == 1 & d2$Answer.Qproper2 == 1 & 
		d2$Answer.Qproper3 == 1 & d2$Answer.Qsub1 == 1 &
		d2$Answer.Qsub2 == 1 & d2$Answer.Qbasic1 == 0 &
		d2$Answer.Qbasic2 == 0 & d2$Answer.Qbasic3 == 0 
	basic <- d2$Answer.Qproper1 == 1 & d2$Answer.Qproper2 == 1 & 
		d2$Answer.Qproper3 == 1 & d2$Answer.Qsub1 == 1 &
		d2$Answer.Qsub2 == 1 & d2$Answer.Qbasic1 == 1 &
		d2$Answer.Qbasic2 == 1 & d2$Answer.Qbasic3 == 1 
} else if (criterion == "unstrictnew") { 
	proper <- (d2$Answer.Qproper1 == 1 & d2$Answer.Qproper2 == 1 & 
		d2$Answer.Qproper3 == 1) & (d2$Answer.Qsub1 == 0 |
		d2$Answer.Qsub2 == 0) & d2$Answer.Qbasic1 == 0 &
		d2$Answer.Qbasic2 == 0 & d2$Answer.Qbasic3 == 0 
	sub <- 	d2$Answer.Qproper1 == 1 & d2$Answer.Qproper2 == 1 & 
		d2$Answer.Qproper3 == 1 & d2$Answer.Qsub1 == 1 &
		d2$Answer.Qsub2 == 1 & d2$Answer.Qbasic1 == 0 &
		d2$Answer.Qbasic2 == 0 & d2$Answer.Qbasic3 == 0 
	basic <- d2$Answer.Qproper1 == 1 & d2$Answer.Qproper2 == 1 & 
		d2$Answer.Qproper3 == 1 & d2$Answer.Qsub1 == 1 &
		d2$Answer.Qsub2 == 1 & (d2$Answer.Qbasic1 == 1 |
		d2$Answer.Qbasic2 == 1 | d2$Answer.Qbasic3 == 1)
} 

d2$w.ans.cat <- "other"
#d2$w.ans.cat[proper] <- "proper"
d2$w.ans.cat[sub] <- "sub"
d2$w.ans.cat[basic] <- "basic"
d2$w.ans.cat <- factor(d2$w.ans.cat,c("proper","sub","basic","other"))
d2 = d2[d2$w.ans.cat != "other",]
# get proportions and bootstrapped CIS
M2 <- data.frame()
for (k in 1:length(levels(d2$w.ans.cat))){
    M2 = rbind(M2, ddply(d2, .(Answer.sample), 
                     function (d) {getPs(d$w.ans.cat, levels(d$w.ans.cat)[k])}))
}
M2$exp = "Turk #2"
```

Plot.

```{r, echo=F}
# plot
ggplot(data=M2[M2$dv == "basic" | M2$dv == "sub",], aes(x=factor(dv), y=p, fill=Answer.sample)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_linerange(aes(ymin=ciwl,ymax=ciul), position=position_dodge(.9)) +
  ylim(0,1) +
  ylab("Prop. participants showing \ngeneralization pattern") +
  xlab("Generalization pattern") +
  ggtitle("Turk Replication #2") +
  theme(text = element_text(size=18),
        plot.title=element_text(size=20, face = "bold"),
        plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(color = 'black'),
        legend.position=c(.85,.8),
        panel.background = element_rect(fill = 'white', colour = 'white')) +
  scale_fill_discrete(name="Sampling\nCondition")

```


Stats 
No difference.
```{r}
d2_counts= table(d2$w.ans.cat, d2$Answer.sample)[2:3,]
chisq.test(d2_counts)
```


<a name="l1"/>
<h3> In Lab Replication </h3>

```{r}
l1 <- read.csv("../data/inlab_replication.csv")
#proper <- l1$basic1_a == 0 & l1$basic2_a == 0 & 
 # l1$basic1_b == 0 & l1$basic2_b == 0 & 
 # (l1$sub1_a == 0 | l1$sub2_a == 0 | l1$sub1_b == 0 | l1$sub2_b == 0)
sub <- l1$basic1_a == 0 & l1$basic2_a == 0 & 
  l1$basic1_b == 0 & l1$basic2_b == 0 & 
  (l1$sub1_a == 1 & l1$sub2_a == 1 & l1$sub1_b == 1 & l1$sub2_b == 1)
basic <- (l1$basic1_a == 1 | l1$basic2_a == 1 | 
            l1$basic1_b == 1 | l1$basic2_b == 1) & 
  (l1$sub1_a == 1 & l1$sub2_a == 1 & l1$sub1_b == 1 & l1$sub2_b == 1)

l1$ans.cat <- "other"
#l1$ans.cat[proper] <- "proper"
l1$ans.cat[sub] <- "sub"
l1$ans.cat[basic] <- "basic"
l1$ans.cat <- factor(l1$ans.cat,c("proper","sub","basic","other"))
l1 = l1[l1$ans.cat != "other",]
# get proportions and bootstrapped CIS
M3 <- data.frame()
for (k in 1:length(levels(l1$ans.cat))){
    M3 = rbind(M3, ddply(l1, .(sample), 
                     function (d) {getPs(d$ans.cat, levels(d$ans.cat)[k])}))
}

M3$exp = "In Lab"

```


Plot.


```{r, echo=F}
# plot
ggplot(data=M3[M3$dv == "basic" | M3$dv == "sub",], aes(x=factor(dv), y=p, fill=sample)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_linerange(aes(ymin=ciwl,ymax=ciul), position=position_dodge(.9)) +
  ylim(0,1) +
  ylab("Prop. participants showing \ngeneralization pattern") +
  xlab("Generalization pattern") +
  ggtitle("In Lab Replication") +
  theme(text = element_text(size=18),
        plot.title=element_text(size=20, face = "bold"),
        plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(color = 'black'),
        # legend.position=c(.85,.8),
        panel.background = element_rect(fill = 'white', colour = 'white')) +
  scale_fill_discrete(name="Sampling\nCondition")
```

Stats 
No difference.
```{r}
l1_counts= table(l1$ans.cat, l1$sample)[2:3,]
chisq.test(l1_counts)
```

X and T data
```{r}
# adults
n_responses = 14 # N=7/condition, 2 responses/participant

prop_sub_teacher= .928 
n_sub_teacher = round(prop_sub_teacher * n_responses)
n_basic_teacher = n_responses - n_sub_teacher 
teacher_xt_data = as.factor(c(rep("sub", n_sub_teacher), rep("basic", n_basic_teacher)))

prop_sub_learner = .357
n_sub_learner = round(prop_sub_learner * n_responses)
n_basic_learner= n_responses - n_sub_learner
learner_xt_data = as.factor(c(rep("sub", n_sub_learner), rep("basic", n_basic_learner)))

#xt_data = data.frame(teacher = teacher_xt_data, learner = learner_xt_data )
xt_data = data.frame(response=c(as.character(teacher_xt_data),as.character(learner_xt_data)))
xt_data$sample[1:14] = "teacher"
xt_data$sample[15:28] = "learner"

# get proportions and bootstrapped CIS
M4 <- data.frame()
for (k in 1:length(levels(learner_xt_data))){
  M4 = rbind(M4, ddply(xt_data, .(sample), 
                     function (d) {getPs(d$response, levels(d$response)[k])}))
}
M4$exp = "X&T (2007b)"

```

```{r, echo=F, eval = F}
# plot
ggplot(data=M4, aes(x=factor(dv), y=p, fill=sample)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_linerange(aes(ymin=ciwl,ymax=ciul), position=position_dodge(.9)) +
  ylim(0,1) +
  ylab("Prop. responses showing \ngeneralization pattern") +
  xlab("Generalization pattern") +
  ggtitle("X and T (2007b)") +
  theme(text = element_text(size=18),
        plot.title=element_text(size=20, face = "bold"),
        plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(color = 'black'),
       # legend.position=c(.85,.8),
        panel.background = element_rect(fill = 'white', colour = 'white')) +
  scale_fill_discrete(name="Sampling\nCondition")


```

Plot of all experiments
```{r, fig.width = 10, echo = F}
names(M)[1] = "sample"
names(M2)[1] = "sample"
allM = rbind(M, M2, M3, M4)

allM$exp <- ordered(as.factor(allM$exp), levels = c( "X&T (2007b)", "Turk #1" ,"Turk #2", "In Lab"  ))

ggplot(data=allM[allM$dv == "basic" | allM$dv == "sub",], 
       aes(x=factor(dv), y=p, fill=sample)) +
  facet_grid(. ~ exp) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_linerange(aes(ymin=ciwl,ymax=ciul), position=position_dodge(.9)) +
  ylim(0,1) +
  ylab("Prop. showing generalization pattern") +
  xlab("Generalization pattern") +
  #ggtitle("X and T (2007b)") +
  theme(text = element_text(size=18),
        plot.title=element_text(size=20, face = "bold"),
        plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(color = 'black'),
       # legend.position=c(.85,.8),
        panel.background = element_rect(fill = 'white', colour = 'white')) +
  scale_fill_discrete(name="Sampling\nCondition")
```

Effect sizes
```{r}
e1 = d.fc(d1$w.ans.cat[d1$w.ans.cat != "other"], d1$Answer.sample[d1$w.ans.cat != "other"])
e2 = d.fc(d2$w.ans.cat[d2$w.ans.cat != "other"], d2$Answer.sample[d2$w.ans.cat != "other"])
e3= d.fc(l1$ans.cat[l1$ans.cat != "other"], l1$sample[l1$ans.cat != "other"])
e4 = d.fc(xt_data$response, xt_data$sample)
```

```{r, echo = F}
es = rbind(e1, e2, e3, e4)
es$exp = c(  "Turk #1" ,"Turk #2", "In Lab","X&T (2007b)")
es$exp<- ordered(as.factor(es$exp), levels = c( "X&T (2007b)", "Turk #1" ,"Turk #2", "In Lab"  ))


ggplot(es, aes(x = exp, y =effect_size, ymin = cill, ymax = ciul)) + 
  geom_pointrange( position=position_dodge(width=0.50), size = 1) + 
  ylab("Cohen's d") + 
  xlab("Experiment") + 
  theme_bw() +
  theme(text = element_text(size=20)) +
  ggtitle("Effect sizes")
  

```












