---
output: html_document
---
<h2>  Xu and Tenenbaum 2007b Replication </h2>
<h3> Supplementary Information </h3>

***
***

**TABLE OF CONTENTS**<br/>
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**[(1) Xu and Tenenabum 2007b (original)](#o)** <br/>
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**[(2) Exp. 1 - online](#t1)** <br/>
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**[(3) Exp. 2 - online](#t2)** <br/>
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**[(4) Exp. 3 - in person](#l1)** <br/>
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**[(5) Exp. 4 - online](#t3)** <br/>
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**[(5) All](#all)** <br/>


This document was created from an R Markdown file. The R Markdown file can be found <a href="https://github.com/mllewis/RC/blob/master/analysis/refComplex_paper_analyses_LF.Rmd" target="_blank"> here</a>. All analyses and plots can be reproduced from the <a href="https://github.com/mllewis/RC/tree/master/data" target="_blank">raw data</a> with the code in this file. This document also contains links to the experimental tasks.

***
***

```{r include = F}

rm(list = ls())

#--Load packages--
library(knitr)
library(boot)
library(ggplot2)
library(plyr)
library(dplyr)

# graphical parameters
fs = 18
ts = 20

get.prop.CIs <- function(d, dv){ 
  prop = sum(d==dv)/length(d)

  # bootstrap across subject proportion responses for each category
  b <- boot(d, function(u, i) table(u[i])[dv]/length(u), R = 1000) 
  ci <- boot.ci(b, type = "perc")  
  ciwl = ci$percent[4]
  ciwu = ci$percent[5]
  
  p.CIS <- data.frame(ciwl = ciwl, ciul = ciwu, w.ans.cat = dv, ps.boot = prop)
  return (p.CIS)
}

theme_set(theme_bw())
themeML = theme(text = element_text(size=fs),
                plot.title=element_text(size=ts, face = "bold"),
                plot.background = element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.border = element_blank(),
                axis.line = element_line(color = 'black')) 

d.fc <- function(response, cond) {

  # http://www.meta-analysis.com/downloads/Meta-analysis%20Converting%20among%20effect%20sizes.pdf
  #https://www.medcalc.net/tests/odds_ratio.php
  response = droplevels(response)
  response <- ordered(response, levels = c( "basic", "sub"))
  cond <- ordered(cond, levels = c( "learner", "teacher"))
  
  #use odds ratioto calculate d
  ns = table(cond, response)
  or = (ns[1]*ns[4])/(ns[2]*ns[3]) 
  cf = sqrt(3)/pi
  effect_size = log(or) * cf #calculate d
  
  # calculate 95 CI
  ## parametrically
  var_lor = (1/ns[1]) + (1/ns[2]) + (1/ns[3]) + (1/ns[4]) # sampling variance of lor
  var_d  = (3/(pi^2)) * var_lor # sampling variance of d
  d_err = sqrt(var_d) * 1.96
  
  cill = effect_size - d_err
  ciul = effect_size + d_err
  
  es <- data.frame(effect_size = effect_size, cill = cill, ciul = ciul)
  
  return (es)
}

opts_chunk$set(echo = T, message = F, warning = F, error = F, cache = F)


```

There are two different criteria possible for categorizing a participant as a subordinate or basic-level generalizer. X&T find that participants respond consistently. 
```{r, echo = F}
# include proper generalizations?
strict = FALSE
proper = FALSE # this only affects plots

print(paste("Strict criteria: ", strict))
```

<a name="o"/>
<h3> Original Xu and Tenenbaum 2007b </h3>

X&T 2007b data - adults
```{r}
N = 14
N_per_condition = N/2 # 7/condition
n_responses = 8 # per participant [(2 sub + 2 basic) x 2 trials]
total_n_responses_per_condition = n_responses * N_per_condition

prop_sub_teacher= .928 
n_sub_teacher = round(prop_sub_teacher * total_n_responses_per_condition)
n_basic_teacher = total_n_responses_per_condition - n_sub_teacher 
teacher_xt_data = as.factor(c(rep("sub", n_sub_teacher),
                              rep("basic", n_basic_teacher)))

prop_sub_learner = .357
n_sub_learner = round(prop_sub_learner * total_n_responses_per_condition)
n_basic_learner= total_n_responses_per_condition - n_sub_learner
learner_xt_data = as.factor(c(rep("sub", n_sub_learner), 
                              rep("basic", n_basic_learner)))

xt_data.adults = data.frame(response=c(as.character(teacher_xt_data),
                                       as.character(learner_xt_data)))
xt_data.adults$Answer.sample[1:total_n_responses_per_condition] = "teacher"
xt_data.adults$Answer.sample[(total_n_responses_per_condition+1):
                               (total_n_responses_per_condition*2)] = "learner"

# get proportions and bootstrapped CIS
M <- data.frame()
for (k in 1:length(levels(learner_xt_data))){
    M = rbind(M, ddply(xt_data.adults, .(Answer.sample), 
                     function (d) {get.prop.CIs(d$response, levels(d$response)[k])}))
}

xt.a.props = M
names(xt.a.props)[names(xt.a.props) == "ps.boot"] = "prop"
xt.a.props$exp ="X&T (2007b)"

# add n's
xt.a.props[xt.a.props$Answer.sample == "teacher" &
           xt.a.props$w.ans.cat == "sub", "n" ] = n_sub_teacher 
xt.a.props[xt.a.props$Answer.sample == "teacher" & 
           xt.a.props$w.ans.cat == "basic", "n"] = n_basic_teacher 
xt.a.props[xt.a.props$Answer.sample == "learner" & 
           xt.a.props$w.ans.cat == "sub", "n" ] = n_sub_learner 
xt.a.props[xt.a.props$Answer.sample == "learner" & 
           xt.a.props$w.ans.cat == "basic", "n" ] = n_basic_learner 
```

X&T 2007b data - children
```{r}
N = 24
N_per_condition = N/2 # 12/condition
n_responses = 8 # per participant [(2 sub + 2 basic) x 2 trials]
total_n_responses_per_condition = n_responses * N_per_condition

prop_sub_teacher= .71
n_sub_teacher = round(prop_sub_teacher * total_n_responses_per_condition)
n_basic_teacher = total_n_responses_per_condition - n_sub_teacher 
teacher_xt_data = as.factor(c(rep("sub", n_sub_teacher),
                              rep("basic", n_basic_teacher)))

prop_sub_learner = .29
n_sub_learner = round(prop_sub_learner * total_n_responses_per_condition)
n_basic_learner= total_n_responses_per_condition - n_sub_learner
learner_xt_data = as.factor(c(rep("sub", n_sub_learner), 
                              rep("basic", n_basic_learner)))

xt_data.children = data.frame(response=c(as.character(teacher_xt_data),
                                       as.character(learner_xt_data)))
xt_data.children$Answer.sample[1:total_n_responses_per_condition] = "teacher"
xt_data.children$Answer.sample[(total_n_responses_per_condition+1):
                               (total_n_responses_per_condition*2)] = "learner"

# get proportions and bootstrapped CIS
M <- data.frame()
for (k in 1:length(levels(learner_xt_data))){
    M = rbind(M, ddply(xt_data.children, .(Answer.sample), 
                     function (d) {get.prop.CIs(d$response, levels(d$response)[k])}))
}

xt.c.props = M
names(xt.c.props)[names(xt.c.props) == "ps.boot"] = "prop"
xt.c.props$exp ="X&T (2007b) children"

# add n's
xt.c.props[xt.c.props$Answer.sample == "teacher" &
           xt.c.props$w.ans.cat== "sub", "n" ] = n_sub_teacher 
xt.c.props[xt.c.props$Answer.sample == "teacher" & 
           xt.c.props$w.ans.cat== "basic", "n"] = n_basic_teacher 
xt.c.props[xt.c.props$Answer.sample == "learner" & 
           xt.c.props$w.ans.cat== "sub", "n" ] = n_sub_learner 
xt.c.props[xt.c.props$Answer.sample == "learner" & 
           xt.c.props$w.ans.cat== "basic", "n" ] = n_basic_learner 
```

```{r, echo = F}
xt = rbind(xt.c.props, xt.a.props)
xt$exp = revalue(xt$exp,c("X&T (2007b) children" = "children",
                          "X&T (2007b)" = "adults"))

ggplot(xt, aes(x=factor(w.ans.cat), y=prop, fill=Answer.sample)) +
  facet_grid(. ~ exp) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_linerange(aes(ymin=ciwl,ymax=ciul), position=position_dodge(.9)) +
  ylim(0,1) +
  ylab("Prop. participants") +
  xlab("Generalization pattern") +
  scale_fill_brewer(name="Sampling\nCondition", palette="Set1") +
  ggtitle("Original Xu and Tenenbaum Data") +
  themeML  
```

<a name="t1"/>
<h3> Experiment 1 </h3>

Read in data and pre-process.
```{r}
t1 = read.csv("../data/turk_replication_1.csv")

# make factors
t1$Answer.sample <- factor(t1$Answer.sample, labels=c('teacher','learner')) # sample0= teacher, sample1=learner
t1$Answer.label <- factor(t1$Answer.label, labels=c('nolabel','label')) # 0=nolabel, 1=label

t1 <- colwise(as.factor)(t1)
```

Filter.
```{r}
# get number of exclusions by category
t1.exclusion.ns = t1 %>%
              summarise(n_noLabelTrials = length(which(Answer.label != 'label')),
                        n_repeatWorkers = length(which(duplicated(workerid))),
                        n_badTraining = length(which(Answer.click1 == "\"false\"" | 
                                                       Answer.click2 == "\"false\"")),
                        n_badGeneralize = length(which(Answer.Qwcheck != 0)),
                        n_badFilter = length(which(Answer.question1 == 'FALSE')))

t1.exclusion.ns

# subset data
t1.f = t1 %>%
       filter(Answer.label == 'label') %>% #remove nolabel trials (run 4)
       filter(!duplicated(workerid)) %>% #participants who completed multiple runs
       filter(Answer.click1 == "\"correct\"" & 
                Answer.click2 == "\"correct\"") %>% #correct training items (learning only)
       filter(Answer.Qwcheck == 0)  %>% #check generalization question
       filter(Answer.question1 == 'TRUE') #filter question

dim(t1)[1] # total
dim(t1.f)[1] # total with exclusions
```

Categorize response patterns based on criterion.
```{r}
sub <- t1.f$Answer.Qwsmm1 == 0 & t1.f$Answer.Qwsmm2 == 0 & 
  t1.f$Answer.Qwsm1 == 1 & t1.f$Answer.Qwsm2 == 1
if (strict){
  basic <- (t1.f$Answer.Qwsmm1 == 1 & t1.f$Answer.Qwsmm2 == 1) &
      t1.f$Answer.Qwsm1 == 1 & t1.f$Answer.Qwsm2 == 1 
} else {
  basic <- (t1.f$Answer.Qwsmm1 == 1 | t1.f$Answer.Qwsmm2 == 1) &
       t1.f$Answer.Qwsm1 == 1 & t1.f$Answer.Qwsm2 == 1 
}

t1.f$w.ans.cat <- "other"
t1.f$w.ans.cat[sub] <- "sub"
t1.f$w.ans.cat[basic] <- "basic"

if (proper){
  #proper <- t1.f$Answer.Qwsmm1 == 0 & t1.f$Answer.Qwsmm2 == 0 & 
  #      (t1.f$Answer.Qwsm1 == 0 & t1.f$Answer.Qwsm2 == 0)
  proper <- t1.f$Answer.Qwsmm1 == 0 & t1.f$Answer.Qwsmm2 == 0 & 
        (t1.f$Answer.Qwsm1 == 0 | t1.f$Answer.Qwsm2 == 0)
  t1.f$w.ans.cat[proper] <- "proper"
  t1.f$w.ans.cat = factor(t1.f$w.ans.cat, levels=c("proper", "sub", "basic", "other"))
} else {
  t1.f$w.ans.cat = factor(t1.f$w.ans.cat, levels=c("sub", "basic", "other"))
}

# filter out other responses
length(which(t1.f$w.ans.cat == "other"))
t1.f = t1.f[t1.f$w.ans.cat != "other",]
t1.f$w.ans.cat = droplevels(t1.f$w.ans.cat)

# get proportions and bootstrapped CIS
M <- data.frame()
for (k in 1:length(levels(t1.f$w.ans.cat))){
    M = rbind(M, ddply(t1.f, .(Answer.sample), 
                     function (d) {get.prop.CIs(d$w.ans.cat, levels(d$w.ans.cat)[k])}))
}

t1.f.props = t1.f %>%
          group_by(Answer.sample, w.ans.cat) %>%
          summarise (n = n()) %>%
          mutate(prop = n / sum(n),
                 exp = "Turk #1") %>%
          left_join(M)
```

```{r, echo = F}
ggplot(t1.f.props, aes(x=factor(w.ans.cat), y=prop, fill=Answer.sample)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_linerange(aes(ymin=ciwl,ymax=ciul), position=position_dodge(.9)) +
  ylim(0,1) +
  ylab("Prop. participants") +
  xlab("Generalization pattern") +
  ggtitle("Turk Replication #1") +
  theme(legend.position=c(.85,.8)) + 
  themeML  +
  scale_fill_brewer(name="Sampling\nCondition", palette="Set1")
```

Stats
```{r}
t1_tab = table(t1.f$w.ans.cat, t1.f$Answer.sample)[c("sub", "basic"),]
chisq.test(t1_tab)
```

<a name="t2"/>
<h3> Experiment #2 </h3>

Read in data and pre-process
```{r}
t2 <- read.csv("../data/turk_replication_2.csv", sep="\t", header=T)
t2  <- t2 [,c(-1:-19,-21:-32,-36,-41:-43,-54:-55,-56)] # remove unnecessary columns

# make factors
t2$Answer.sample <- factor(t2$Answer.sample, labels=c('teacher','learner')) # sample0 = teacher, sample1=learner
t2 <- colwise(as.factor)(t2)
```

Filter.
```{r}
# get number of exclusions by category
t2.exclusion.ns = t2 %>%
              summarise(n_badTraining = length(which(Answer.click1 != "\"correct\"" |
                                                       Answer.click2 != "\"correct\"")),
                        n_badGeneralize = length(which(Answer.Qcheck1 != 0 | Answer.Qcheck2 != 0)),
                        n_badFilter = length(which(Answer.question3 != 'true' | Answer.question4 !='true')))
t2.exclusion.ns

# subset data
t2.f = t2 %>%
       filter(Answer.click1 == "\"correct\"" &
                Answer.click2 == "\"correct\"") %>% # take out those who click on wrong training items
      filter(Answer.Qcheck1 == 0 & Answer.Qcheck2 == 0) %>% # take out if missed check generalization question
      filter(Answer.question3 == 'true' & Answer.question4 =='true')  # take out those who missed filter question

dim(t2)[1] # total
dim(t2.f)[1] # total with exclusions
```


Categorize response patterns based on criterion.
```{r}
sub <-  t2.f$Answer.Qproper1 == 1 & t2.f$Answer.Qproper2 == 1 & 
  t2.f$Answer.Qproper3 == 1 & t2.f$Answer.Qsub1 == 1 &
  t2.f$Answer.Qsub2 == 1 & t2.f$Answer.Qbasic1 == 0 &
  t2.f$Answer.Qbasic2 == 0 & t2.f$Answer.Qbasic3 == 0 

if (strict){
  basic <- t2.f$Answer.Qproper1 == 1 & t2.f$Answer.Qproper2 == 1 & 
    t2.f$Answer.Qproper3 == 1 & t2.f$Answer.Qsub1 == 1 &
    t2.f$Answer.Qsub2 == 1 & t2.f$Answer.Qbasic1 == 1 &
    t2.f$Answer.Qbasic2 == 1 & t2.f$Answer.Qbasic3 == 1 
} else {
  basic <- t2.f$Answer.Qproper1 == 1 & t2.f$Answer.Qproper2 == 1 & 
    t2.f$Answer.Qproper3 == 1 & t2.f$Answer.Qsub1 == 1 &
    t2.f$Answer.Qsub2 == 1 & (t2.f$Answer.Qbasic1 == 1 |
    t2.f$Answer.Qbasic2 == 1 | t2.f$Answer.Qbasic3 == 1)
}

t2.f$w.ans.cat <- "other"
t2.f$w.ans.cat[sub] <- "sub"
t2.f$w.ans.cat[basic] <- "basic"

if(proper){
  proper <- (t2.f$Answer.Qproper1 == 1 & t2.f$Answer.Qproper2 == 1 & 
    t2.f$Answer.Qproper3 == 1) & t2.f$Answer.Qsub1 == 0 &
    t2.f$Answer.Qsub2 == 0 & t2.f$Answer.Qbasic1 == 0 &
    t2.f$Answer.Qbasic2 == 0 & t2.f$Answer.Qbasic3 == 0 
    
    t2.f$w.ans.cat[proper] <- "proper"
    t2.f$w.ans.cat = factor(t2.f$w.ans.cat, levels=c("proper", "sub", "basic", "other"))

} else {
  t2.f$w.ans.cat = factor(t2.f$w.ans.cat, levels=c("sub", "basic", "other"))
}

# filter out "other" responses
length(which(t2.f$w.ans.cat == "other"))
t2.f = t2.f[t2.f$w.ans.cat != "other",]
t2.f$w.ans.cat = droplevels(t2.f$w.ans.cat)

# get proportions and bootstrapped CIS
M <- data.frame()
for (k in 1:length(levels(t2.f$w.ans.cat))){
    M = rbind(M, ddply(t2.f, .(Answer.sample), 
                     function (d) {get.prop.CIs(d$w.ans.cat, levels(d$w.ans.cat)[k])}))
}

t2.f.props = t2.f %>%
          group_by(Answer.sample, w.ans.cat) %>%
          summarise (n = n()) %>%
          mutate(prop = n / sum(n),
                 exp = "Turk #2") %>%
          left_join(M)
```

```{r, echo=F}
ggplot(t2.f.props, aes(x = factor(w.ans.cat), y = prop, fill = Answer.sample)) +
  geom_bar(stat ="identity", position = position_dodge()) +
  geom_linerange(aes(ymin = ciwl, ymax = ciul), position = position_dodge(.9)) +
  ylim(0,1) +
  ylab("Prop. participants") +
  xlab("Generalization pattern") +
  ggtitle("Turk Replication #2") +
  themeML + 
  theme(legend.position=c(.85, .8)) + 
  scale_fill_brewer(name="Sampling\nCondition", palette="Set1")
```

Stats 
```{r}
t2_tab = table(t2.f$w.ans.cat, t2.f$Answer.sample)[c("sub", "basic"),]
chisq.test(t2_tab)
```


<a name="l1"/>
<h3> Experiment 3 - In Lab Replication </h3>

```{r}
l1 <- read.csv("../data/inlab_replication.csv")

# make factors
l1 <- colwise(as.factor)(l1)
names(l1)[names(l1) == "sample"] = "Answer.sample"

```

Filter.
```{r}
l1.exclusion.ns = l1 %>%
                  summarise(n_badTraining = length(which(t2_a == 0 | t3_a == 0 |
                                                           t2_b == 0 | t2_b == 0)))
l1.exclusion.ns

# subset data
l1.f = l1 %>%
       filter(t2_a == 1 & t3_a == 1 & t2_b == 1 & t2_b == 1)

dim(l1)[1] # total
dim(l1.f)[1] # total with exclusions
```

Categorize response patterns based on criterion.
```{r}
sub <- l1.f$basic1_a == 0 & l1.f$basic2_a == 0 & 
       l1.f$basic1_b == 0 & l1.f$basic2_b == 0 & 
       (l1.f$sub1_a == 1 & l1.f$sub2_a == 1 & 
          l1.f$sub1_b == 1 & l1.f$sub2_b == 1)
if (strict){
    basic <- (l1.f$basic1_a == 1 & l1.f$basic2_a == 1 &
            l1.f$basic1_b == 1 & l1.f$basic2_b == 1) & 
           (l1.f$sub1_a == 1 & l1.f$sub2_a == 1 & 
              l1.f$sub1_b == 1 & l1.f$sub2_b == 1)
  
} else {
  basic <- (l1.f$basic1_a == 1 | l1.f$basic2_a == 1 | 
            l1.f$basic1_b == 1 | l1.f$basic2_b == 1) & 
           (l1.f$sub1_a == 1 & l1.f$sub2_a == 1 & 
              l1.f$sub1_b == 1 & l1.f$sub2_b == 1)
}

l1.f$w.ans.cat <- "other"
l1.f$w.ans.cat[sub] <- "sub"
l1.f$w.ans.cat[basic] <- "basic"

if (proper){
  proper <- l1.f$basic1_a == 0 & l1.f$basic2_a == 0 & 
            l1.f$basic1_b == 0 & l1.f$basic2_b == 0 & 
            (l1.f$sub1_a == 0 | l1.f$sub2_a == 0 |
               l1.f$sub1_b == 0 | l1.f$sub2_b == 0)
  l1.f$w.ans.cat[proper] <- "proper"
  l1.f$w.ans.cat <- factor(l1.f$w.ans.cat,c("proper","sub","basic","other"))
} else {
  l1.f$w.ans.cat <- factor(l1.f$w.ans.cat,c("sub","basic","other"))
}

# filter out "other"" responses
length(which(l1.f$w.ans.cat  == "other"))
l1.f = l1.f[l1.f$w.ans.cat != "other",]
l1.f$w.ans.cat = droplevels(l1.f$w.ans.cat)

# get proportions and bootstrapped CIS
M <- data.frame()
for (k in 1:length(levels(l1.f$w.ans.cat))){
    M = rbind(M, ddply(l1.f, .(Answer.sample), 
                     function (d) {get.prop.CIs(d$w.ans.cat, levels(d$w.ans.cat)[k])}))
}

l1.f.props = l1.f %>%
          group_by(Answer.sample, w.ans.cat) %>%
          summarise (n = n()) %>%
          mutate(prop = n / sum(n),
                 exp = "In Lab") %>%
          left_join(M)

# re-order levels so consistent with other exps
l1.f.props$Answer.sample <- ordered(l1.f.props$Answer.sample, 
                    levels = c("teacher", "learner"))
```

```{r, echo = F}
ggplot(l1.f.props, aes(x=factor(w.ans.cat), y = prop, fill = Answer.sample)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_linerange(aes(ymin=ciwl, ymax=ciul), position = position_dodge(.9)) +
  ylim(0,1) +
  ylab("Prop. participants") +
  xlab("Generalization pattern") +
  ggtitle("In Lab") +
  themeML + 
  scale_fill_brewer(name="Sampling\nCondition", palette="Set1")
```

Stats
```{r}
l1_tab = table(l1.f$w.ans.cat, l1.f$sample)[c("sub", "basic"),]
chisq.test(l1_tab)
```

<a name="t3"/>
<h3> Expeiment 4 - Turk Replication #3 </h3>

Read in data and pre-process
```{r}
t3 <- read.csv("../data/turk_replication_3.csv")

# make factors
t3$Answer.sample <- factor(t3$Answer.sample, labels=c('teacher','learner')) # sample0 = teacher, sample1=learner
t3 <- colwise(as.factor)(t3)
```

Filter.
```{r}
t3.exclusion.ns = t3 %>%
              summarise(n_badTraining = length(which(Answer.click1 != "\"correct\"" | 
                                                       Answer.click2 != "\"correct\"")),
                        n_badGeneralize = length(which(Answer.Qcheck1 != 0 | Answer.Qcheck2 != 0)),
                        n_badFilter = length(which(Answer.question1 != 'TRUE' | Answer.question2 !='TRUE'| 
                                Answer.question3 != 'TRUE' | Answer.question4 !='TRUE')))
t3.exclusion.ns

# subset data
t3.f= t3 %>%
      filter(Answer.click1 == "\"correct\"" & 
                Answer.click2 == "\"correct\"") %>% # take out those who click on wrong training items
      filter(Answer.Qcheck1 == 0 & Answer.Qcheck2 == 0) %>% # take out if missed check generalization question
      filter(Answer.question1 == 'TRUE' & Answer.question2 =='TRUE' & 
            Answer.question3 == 'TRUE' & Answer.question4 =='TRUE')  # take out those who missed filter question

dim(t3)[1] # total
dim(t3.f)[1] # total with exclusions
```


Categorize response patterns based on criterion.
```{r}
sub <-  t3.f$Answer.Qproper1 == 1 & t3.f$Answer.Qproper2 == 1 & 
    t3.f$Answer.Qproper3 == 1 & t3.f$Answer.Qsub1 == 1 &
    t3.f$Answer.Qsub2 == 1 & t3.f$Answer.Qbasic1 == 0 &
    t3.f$Answer.Qbasic2 == 0 & t3.f$Answer.Qbasic3 == 0 

if (strict){
  basic <- t3.f$Answer.Qproper1 == 1 & t3.f$Answer.Qproper2 == 1 & 
    t3.f$Answer.Qproper3 == 1 & t3.f$Answer.Qsub1 == 1 &
    t3.f$Answer.Qsub2 == 1 & t3.f$Answer.Qbasic1 == 1 &
    t3.f$Answer.Qbasic2 == 1 & t3.f$Answer.Qbasic3 == 1 
} else {
  basic <- t3.f$Answer.Qproper1 == 1 & t3.f$Answer.Qproper2 == 1 & 
      t3.f$Answer.Qproper3 == 1 & t3.f$Answer.Qsub1 == 1 &
      t3.f$Answer.Qsub2 == 1 & (t3.f$Answer.Qbasic1 == 1 |
      t3.f$Answer.Qbasic2 == 1 | t3.f$Answer.Qbasic3 == 1)
}

t3.f$w.ans.cat <- "other"
t3.f$w.ans.cat[sub] <- "sub"
t3.f$w.ans.cat[basic] <- "basic"

if (proper){
  proper <- (t3.f$Answer.Qproper1 == 1 & t3.f$Answer.Qproper2 == 1 & 
            t3.f$Answer.Qproper3 == 1) & t3.f$Answer.Qsub1 == 0 &
            t3.f$Answer.Qsub2 == 0 & t3.f$Answer.Qbasic1 == 0 &
            t3.f$Answer.Qbasic2 == 0 & t3.f$Answer.Qbasic3 == 0 
  
  t3.f$w.ans.cat[proper] <- "proper"
  t3.f$w.ans.cat = factor(t3.f$w.ans.cat, levels=c("proper", "sub", "basic", "other"))
} else { 
  t3.f$w.ans.cat = factor(t3.f$w.ans.cat, levels=c("sub", "basic", "other"))
}

# filter out "other"" responses
length(which(t3.f$w.ans.cat == "other"))
t3.f = t3.f[t3.f$w.ans.cat != "other",]
t3.f$w.ans.cat = droplevels(t3.f$w.ans.cat)

# get proportions and bootstrapped CIS
M <- data.frame()
for (k in 1:length(levels(t3.f$w.ans.cat))){
    M = rbind(M, ddply(t3.f, .(Answer.sample), 
                     function (d) {get.prop.CIs(d$w.ans.cat, levels(d$w.ans.cat)[k])}))
}

t3.f.props = t3.f %>%
          group_by(Answer.sample, w.ans.cat) %>%
          summarise (n = n()) %>%
          mutate(prop = n / sum(n),
                 exp = "Turk #3") %>%
          left_join(M)
```

```{r}
ggplot(t3.f.props, aes(x=factor(w.ans.cat), y=prop, fill=Answer.sample)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_linerange(aes(ymin=ciwl,ymax=ciul), position=position_dodge(.9)) +
  ylim(0,1) +
  ylab("Prop. participants") +
  xlab("Generalization pattern") +
  ggtitle("Turk Replication #3") +
  themeML + 
  theme(legend.position=c(.85,.8)) + 
    scale_fill_brewer(name="Sampling\nCondition", palette="Set1")
```

Stats
```{r}
t3_tab = table(t3.f$w.ans.cat, t3.f$Answer.sample)[c("sub", "basic"),]
chisq.test(t3_tab)
```

<a name="all"/>
<h3> All experiments </h3>

```{r, fig.width = 10, echo = F}
# bind all props together
lf.props = rbind(t1.f.props, t2.f.props, t3.f.props, l1.f.props)
lf.props$ps.boot <- NULL
all.props= rbind(lf.props, xt.a.props)

all.props$exp <- ordered(as.factor(all.props$exp), 
                    levels = c( "X&T (2007b)", "Turk #1", 
                                "Turk #2", "In Lab", "Turk #3"))

all.props$exp = revalue(all.props$exp, c("X&T (2007b)" = "X&T (2007b)", "Turk #1" = "Exp. 1",
                                "Turk #2" = "Exp. 2", "In Lab" = "Exp. 3", "Turk #3" = "Exp. 4"))

all.props$w.ans.cat  = revalue(all.props$w.ans.cat , c("sub" = "sub."))

#pdf("../../writeup/figures/FIG_2.pdf", height = 4, width = 12)
ggplot(all.props[all.props$w.ans.cat == "basic" | all.props$w.ans.cat == "sub.",],      
       aes(x=w.ans.cat, y=prop, fill = Answer.sample)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_linerange(aes(ymin=ciwl,ymax=ciul), position=position_dodge(.9)) +
  facet_grid(. ~ exp) +
  ylim(0, 1) +
  ylab("Prop. Participants") +
  xlab("Generalization Pattern") +
  themeML + 
  scale_fill_brewer(name="Sampling\nCondition", palette="Set1")
#dev.off()

```

Effect sizes
```{r}
t1.f.es = d.fc(t1.f$w.ans.cat, t1.f$Answer.sample)
t2.f.es= d.fc(t2.f$w.ans.cat, t2.f$Answer.sample)
t3.f.es = d.fc(t3.f$w.ans.cat, t3.f$Answer.sample)
l1.f.es= d.fc(l1.f$w.ans.cat, l1.f$Answer.sample)
xt.a.es = d.fc(xt_data.adults$response, xt_data.adults$Answer.sample)
xt.c.es = d.fc(xt_data.children$response, xt_data.children$Answer.sample)
```

```{r}
all.es = rbind(t1.f.es, t2.f.es, t3.f.es, l1.f.es, xt.a.es)
all.es$exp = c("Turk #1" ,"Turk #2", "Turk #3", "In Lab",
               "X&T (2007b)")
all.es$exp<- ordered(as.factor(all.es$exp), 
                     levels = c("X&T (2007b)", "Turk #1" ,"Turk #2", 
                                  "In Lab", "Turk #3"))

all.es$exp = revalue(all.es$exp, c("X&T (2007b)" = "X&T (2007b)", "Turk #1" = "Exp. 1",
                                "Turk #2" = "Exp. 2", "In Lab" = "Exp. 3", "Turk #3" = "Exp. 4"))

#pdf("../../writeup/figures/FIG_3.pdf", height = 4, width = 4)
ggplot(all.es, aes(x = exp, y = effect_size, ymin = cill, ymax = ciul)) + 
  geom_pointrange(position=position_dodge(width = 0.25), size = .8) + 
  ylab("Effect Size") + 
  xlab("Experiment") + 
  geom_hline(y=0, linetype = "dotted") +
  theme(text=element_text(size=14)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#dev.off()
```

# how to calculate errors bars -- XT do it over responses, I'm doing it over participants

